Excuse me, do you have a moment to talk about version control?

### 2017-05-18 README.Rmd
Don't include the output-format-detecting chunk

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- affiliation: RStudio and the Department of Statistics, University of British Columbia
  name: Jennifer Bryan
  thanks: The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton and Colin Rundel.
blinded: 0
output:
  rticles::asa_article:
    pandoc_args: --listings
  github_document:
    toc: yes
keywords: version control
abstract: Abstract abstract abstract.
---

```{r}
is_github_document <-
  knitr::opts_knit$get("rmarkdown.pandoc.to") == "markdown_github"
```

>>>>

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- affiliation: RStudio and the Department of Statistics, University of British Columbia
  name: Jennifer Bryan
  thanks: The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton and Colin Rundel.
blinded: 0
output:
  github_document:
    toc: yes
  rticles::asa_article:
    pandoc_args: --listings
keywords: version control
abstract: Abstract abstract abstract.
---

```{r include = FALSE}
is_github_document <-
  knitr::opts_knit$get("rmarkdown.pandoc.to") == "markdown_github"
```
